\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{parskip} % Adds space between paragraphs automatically
\usepackage{ifthen}

% --- LOAD SECRETS ---
\IfFileExists{personal.tex}{\input{personal}}{\input{personal_dummy}}

% --- LOGIC GATE ---
\ifthenelse{\equal{\cvMode}{OPS}}
    { \newcommand{\targetRole}{\titleOPS} }
    { \newcommand{\targetRole}{\titleSRE} }

% --- SETUP MARGINS ---
\geometry{
  top=2cm,
  bottom=2cm,
  left=2.5cm,
  right=2.5cm
}

% --- COLORS (Matching your likely CV dark blue/grey) ---
\definecolor{primary}{HTML}{2E2E2E} % Dark Grey
\definecolor{accent}{HTML}{0E5484}  % Professional Blue

\begin{document}
\color{primary}

% --- HEADER ---
{\huge \textbf{\myFirstName \ \myLastName}} \hfill \today \\
\vspace{0.2cm}
{\color{accent} \faPhone \ \myPhone} \quad \textbullet \quad
{\color{accent} \faEnvelope \ \myEmail} \quad \textbullet \quad
{\color{accent} \faLinkedin \ \myLinkedin}
\vspace{0.3cm}
\hrule
\vspace{1cm}

% --- RECIPIENT BLOCK ---
\textbf{To: The Hiring Manager} \\
KW International (Vietnam) \\
\vspace{0.5cm}

\textbf{Subject: Application for Operations Senior - Nguyen Vu Minh}

Dear Hiring Manager,

I am writing to express my strong interest in the Operations Senior position at KW International (Vietnam).

With over 10 years of experience spanning Logistics Operations (TNT Express) and Technical System Architecture, I am looking to pivot my career back into the heart of supply chain management. I understand that modern logistics requires more than just transactional service; it requires a robust, system-driven partnership model. I believe my unique blend of operational experience and technical discipline makes me the ideal candidate to execute this vision.

\vspace{0.3cm}
\textbf{Why a Technical Lead for Operations?}

In today's global supply chain, reliability is a data problem. My recent experience as a Technical Lead has taught me that the best systems are "invisible"—they guide users to the right result without friction. I aim to bring this "Systems Thinking" mindset to KW’s operations:

\begin{itemize}
    \item \textbf{From "Heroics" to "Habits":} I believe that a scalable operation cannot rely on individual staff working harder; it must rely on smarter workflows. At N2N-AFE, I architected centralized digital workflows to replace manual tracking, reducing human error and ensuring no customer request fell through the cracks.
    
    \item \textbf{Logistics DNA:} My 6 years at TNT Express gave me a deep respect for the physical reality of operations—from Airway Bills to Customs clearance. I speak the language of logistics, but I now have the tools of a software architect to solve its problems.
    
    \item \textbf{Vendor \& System Integration:} I have extensive experience acting as the bridge between business goals and technical vendors. I can ensure that the tools KW utilizes actually serve the staff on the ground, enhancing efficiency rather than adding complexity.
\end{itemize}

\vspace{0.3cm}
\textbf{My Commitment}

I am not just looking for a role; I am looking for a mission. I aim to build the operational "backbone" that ensures high-level strategies are executed flawlessly on the ground. My goal is to help build a KW branch where service quality is guaranteed by the system, ensuring consistency and trust for every client.

I have attached my CV for your review. I welcome the opportunity to discuss how my background in systems and logistics can contribute to the success of the KW team.

Sincerely,

\vspace{1cm} % Space for signature if printed

\textbf{Nguyen Vu Minh}

\end{document}
