\sectionTitle{Professional Experience}{\faSuitcase}
\begin{experiences}
    \experience
        {Present}
        {IT Coordinator}
        {N2N-AFE (Hong Kong) Limited}
        {Ho Chi Minh City}
        {Aug 2021}
        {
            \begin{itemize}
                \item \textbf{Technical Consultation:} Acted as the primary bridge between non-technical stakeholders and the engineering team,
                    translating business requirements into technical specs for the Jira-base workflow system.
                \item Engineered automated resilience pipelines for system upgrades and log aggregation,
                    reducing troubleshooting latency by 50\%.
                \item Architected and deployed a new Jira-base addendum management system, replacing a manual Excel precess.
                    This increased customer follow-up efficiency by 90\% and reduced training time by 50\%.
                \item Performed Tire 3 diagnostics on complex SQL (Oracle, MS SQL) statements to identify data errors, reducing troubleshooting time by 40\%.
                \item Contributed to secure network architecture reviews and firewall policy tuning, reducing system latency by 20\% in a production environment.
            \end{itemize}
        }
        {Resilience, Automation, SQL, Jira}

    \emptySeparator

    \experience
        {Aug 2021}
        {IT Supervisor}
        {WMC Central \& Bakery Kitchen Company}
        {Ho Chi Minh City}
        {Oct 2018}
        {
            \begin{itemize}
                \item \textbf{Talent Development:} Mentored junior staff and evaluated technical vendor capabilities to ensure project aligment with business goals.
                \item Monitored and improved data warehousing techniques (data recall, segmentation), increasing non-technical staff productivity by 20\%.
                \item Streamlined data flow precesses, reducing data redundancy by 25\% and improving database integrity.
                \item Implemented an efficient ticketing system to monitor service desk tickets and track incident resolution.
            \end{itemize}
        }
        {Data Warehousing, Leadership, Process Optimization}

    \emptySeparator

    \experience
        {Oct 2018}
        {IT Supervisor}
        {P. Dussmann Vietnam Co., Ltd.}
        {Ho Chi Minh City}
        {Sep 2016}
        {
            \begin{itemize}
                \item Led systems design and architecture for business-critical ERP projects (BOM, purchasing, warehouse management).
                \item Provided Tier 2/3 technical support and application troubleshooting for over 500 end-users.
                \item Administered all aspects of Active Directory group policy and user management.
                \item Oversaw execution of system/software upgrades, establishing roll out plans and infrastructure prep.
            \end{itemize}
        }
        {ERP, System Design, Active Directory}

    \emptySeparator

    \experience
        {Aug 2016}
        {Customer IT Executive (CIT)}
        {TNT Vietrans Express Worldwide}
        {Ho Chi Minh City}
        {Jan 2010}
        {
            \begin{itemize}
                \item Automated daily report generation and streamlined data input for Salesforce (CRM), increasing workflow efficiency.
                \item Developed a custom application to generate airway bills, deployed for all of TNT Vietnam.
                \item Provided direct technical support to external clients for proprietary CIT software products.
            \end{itemize}
        }
        {CRM, Automation, Customer Support}

    \emptySeparator

    \experience
        {2010}
        {IT Support Specialist}
        {Viet Quoc \& Nam Viet Securities}
        {Ho Chi Minh City}
        {Prior}
        {
            \begin{itemize}
                \item Implemented and maintained network security strategies for the internal trading network.
                \item Responsible for network planning, design, security, and optimization to ensure maximum system uptime.
                \item Created detailed network topology documentation (physical/logical diagrams, IP schemes).
            \end{itemize}
        }
        {Network Security, Trading Systems, Infrastructure}

\end{experiences}
