\sectionTitle{Professional Experience}{\faSuitcase}
\begin{experiences}
    \experience
        {Present}
        {IT Coordinator / Operations Technical Lead (Focus: Defining the Process \& System Architecture)}
        {N2N-AFE (Hong Kong) Limited}
        {Ho Chi Minh City}
        {Aug 2021}
        {
            \begin{itemize}
                \item \textbf{Architected and deployed a Jira-based Operations Workflow,} replacing manual Excel tracking for the entire branch.
                    This centralized customer follow-up data, reducing information silos and improving team response times.
                \item \textbf{Led the "Service Provision" strategy} for internal tools, ensuring technical solutions aligned with business speed.
                    Successfully migrated the team to new standards with zero operational downtime.
                \item \textbf{Managed System Integration} between business requirements and engineering reality,
                    acting as the primary translator to ensure deliverables met operational goals.
            \end{itemize}
        }
        {Resilience, Automation, SQL, Jira}

    \emptySeparator

    \experience
        {Aug 2021}
        {IT Supervisor / Supply Chain Data Analyst (Focus: Inventory Integrity \& Warehouse Logic)}
        {WMC Central \& Bakery Kitchen Company}
        {Ho Chi Minh City}
        {Oct 2018}
        {
            \raggedright
            \begin{itemize}
                \item \textbf{Optimized Warehouse Operations:} Partnered with the Documentation Team to automate the "Order-to-Inventory" data flow.
                    Created validation scripts to cross-check "Received Orders" against "Warehouse Data," reducing inventory discrepancies.
                \item \textbf{Streamlined Procurement Data:} Utilized data analysis to convert "Received Material" data into accurate "Placement Orders,"
                    eliminating manual data entry errors in the supply chain.
                \item \textbf{Enhanced Data Visibility:} Improved data warehousing techniques to give non-technical staff faster access to accurate inventory levels,
                    directly supporting daily operational decisions.
            \end{itemize}
        }
        {Data Warehousing, Leadership, Process Optimization}

    \emptySeparator

    \experience
        {Oct 2018}
        {IT Supervisor}
        {P. Dussmann Vietnam Co., Ltd.}
        {Ho Chi Minh City}
        {Sep 2016}
        {
            \raggedright
            \begin{itemize}
                \item Led systems design and architecture for business-critical ERP projects (BOM, purchasing, warehouse management).
                \item Provided Tier 2/3 technical support and application troubleshooting for over 500 end-users.
                \item Administered all aspects of Active Directory group policy and user management.
                \item Oversaw execution of system/software upgrades, establishing roll out plans and infrastructure prep.
            \end{itemize}
        }
        {ERP, System Design, Active Directory}

    \emptySeparator

    \experience
        {Aug 2016}
        {Customer IT Executive (CIT) / Automation Specialist (Focus: The "User Experience" \& Error Reduction)}
        {TNT Vietrans Express Worldwide}
        {Ho Chi Minh City}
        {Jan 2010}
        {
            \begin{itemize}
                \item \textbf{Automated "Last Mile" Data Entry:} Developed custom AutoHotkey automation tools to overlay the legacy Airway Bill system.
                    This acted as an interactive "User Guide," guiding admins to the correct input fields and reducing data entry errors by 50\%
                \item \textbf{Solved "Unscannable" Cargo Issues:} Engineered a re-printing solution for damaged/unclear Airway Bills,
                    allowing Operations teams to scan barcodes instantly instead of manual typing, significantly speeding up cargo processing.
                \item \textbf{Sales Intelligence Automation:} Created data extraction scripts to pull real-time reports from legacy terminal systems,
                    empowering the Sales team with actionable data without requiring manual system navigation.
            \end{itemize}
        }
        {CRM, Automation, Customer Support}

    \emptySeparator

    \experience
        {2010}
        {IT Support Specialist}
        {Viet Quoc \& Nam Viet Securities}
        {Ho Chi Minh City}
        {Prior}
        {
            \begin{itemize}
                \item Implemented and maintained network security strategies for the internal trading network.
                \item Responsible for network planning, design, security, and optimization to ensure maximum system uptime.
                \item Created detailed network topology documentation (physical/logical diagrams, IP schemes).
            \end{itemize}
        }
        {Network Security, Trading Systems, Infrastructure}

\end{experiences}
